Evaluating Sound Similarity Metrics for Differentiable, Iterative Sound-Matching

### 2025-08-21 revised_main.tex
Updates from Overleaf

Particularly in earlier works, frequency/amplitude modulators (\gls{FM}/\gls{AM}) has been the synthesizer of choice in sound-matching~\cite{horner1993machine,mitchell2007evolutionary,vahidi2023mesostructures}. This synthesis method is simple to implement, yet very expressive~\cite{chowning1973synthesis}. One of the earliest foundational sound-matching works is the analytical approach by Justice~\cite{justice1979analytic} toward the decomposition and recreation of sounds with FM synthesis using one carrier, one modulator, and the corresponding envelopes:
\[ f(t) = I_c(t) \cos(\omega_c t + I_m(t) \cos(\omega_m t))
\]
Where $f(t)$ is the output signal, $I_c(t)$ is the carrier amplitude, $\omega_c$ is the carrier frequency, and $I_m(t)$ and $\omega_m$ are the envelope and frequency for the modulator~\cite{justice1979analytic}.

@@

Given the different attributes discussed thus far, Table~\ref{tab:summary} contains an overview of relevant literature, covering important works in sound-matching. A more detailed historical analysis of past and current trends in sound-matching can be discussed.

>>>>

Particularly in earlier works, frequency/amplitude modulators (\gls{FM}/\gls{AM}) has been the synthesizer of choice in sound-matching~\cite{horner1993machine,mitchell2007evolutionary,vahidi2023mesostructures}. This synthesis method is simple to implement, yet very expressive~\cite{chowning1973synthesis}. A common implementation is the use of one carrier, one modulator, and the corresponding envelopes:
\[ f(t) = I_c(t) \cos(\omega_c t + I_m(t) \cos(\omega_m t))
\]
Where $f(t)$ is the output signal, $I_c(t)$ is the carrier amplitude, $\omega_c$ is the carrier frequency, and $I_m(t)$ and $\omega_m$ are the envelope and frequency for the modulator~\cite{justice1979analytic}.

@@

Given the different attributes discussed thus far, Table~\ref{tab:summary} contains an overview of important relevant literature. This leads us to a more detailed historical analysis of past works in sound-matching.
